\sysfull

### 2018-04-14 paper/intro.tex
sinan figure re-added to intro
minor changes
remove the history our algo and its fig
intro figure text cleaned up

@@

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/coalescing-is}
    \caption{\textbf{An execution of three
statically-defined tasks without (top) and with (bottom) dynamic
coalescing.} Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
    \label{fig:coalesce}
\end{wrapfigure}

>>>>

%%%%%%%%%%%%%%%%%%%%%% IMPORTANT INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SRAM read/write latency is in the order of 8ns 		 [ Intermittent computation without hardware support of programmer intervention]
% FRAM read/write latency is in the orfer of 60ns/100ns  [Texas Instrument MSP430FR573x DataSheet]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/graffle/intro-figure.pdf} By Sinan
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits and buffering updates to non-volatile (NV) variables in volatile (V) memory.}
    \label{fig:coalesce}
\end{wrapfigure}
